Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-17 MSc-dissertation.tex
New para
New fix
Fig fix

\begin{abstract}
    This is the bit where you summarise what is in your thesis.
\end{abstract}

@@

\input{conclusion/future_works.tex}

>>>>

\begin{abstract}
    Zebrafish can regenerate the spinal cord after injury, and possibly recover swimming function. The regeneration is a complex biological process with many interacting parts. We modelled the dynamics of two cell and two molecules that participate in the regeneration, according to the existing experimental findings\cite{ref:Tsarouchas}, and wished to explore uncertainties in their parameter estimates.

    As an Approximate Bayesian Computation (ABC) method, ABC SMC (Sequential Monte-Carlo) method was implemented on the proposed models to approximate the posteriors the parameters. We conducted some preliminary experiments to study the ability of inference and robustness of the algorithm before we performed the inference of parameters and model comparison using the same inference framework. The result shows well-inferred parameters and a preferred model with high model probability.

    The algorithm implementation shows a decent scaling-up performance; however, problems with local optimum and some other uncertainties were also found. Suggestions on the implementation options and ABC SMC settings were made to avoid these problems.
\end{abstract}

@@

### 2020-08-17 implementation/implementation.tex
Fig fix

    \caption{Simulated data from the last population of model 3, 4 and 5. Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small)}
    \label{fig:resultCurve345}

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{0.8\hsize}{!}{\includegraphics{fig/pc_pie_all.png}}
    \end{center}

    \caption[TODO]{Fraction of the length of PCs explained by parameters}
    \label{fig:pc_pie}
\end{figure}

>>>>

    \caption[Simulated data from the last population of model 3, 4 and 5]{Simulated data from the last population of model 3, 4 and 5. Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small)}
    \label{fig:resultCurve345}

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{0.8\hsize}{!}{\includegraphics{fig/pc_pie.png}}
    \end{center}

    \caption[Fraction of the length of PCs explained by parameters]{Fraction of the length of PCs explained by parameters. Portions less than 2\% are not labelled}
    \label{fig:pc_pie}
\end{figure}
